
Abbate, Janet, \emph{Inventing the Internet} (Cambridge: MIT Press, 1999)
Abbate, Janet, \emph{Inventing the Internet} (Cambridge: MIT Press, 1999)
Brautigan, Richard. "All Watched Over by Machines of Loving Grace". San Francisco. The Communication Company. 1967. Print.
Breen, C. and Dahlbom, C. A. "Signaling Systems for Control of Telephone Switching," \emph{The Bell System Technical Journal} 39:6. Nov 1960.
Chaos Computer Congress. "Hackerethik," Berlin 2013. http://ccc.de/de/hackerethik
Coleman, Gabriela. \emph{Coding Freedom.} Princeton: Princeton University Press, 2013, pg17.
Digital Equipment Corporation \emph{Digital Equipment Corporation: Nineteen Fifty-Seven to the Present.} (DEC Press. 1978) pg. 3
DIzzIE, "Why I Steal from Libraries" (Textfiles.com 2007) http://textfiles.com/uploads/diz-libraries.txt} 
\emph{Government Computer Security: Weak Computer Security in the Government: Is the Public at Risk with the U.S. Permanent Subcommittee on Investigations of the Senate Committee on Governmental Affairs}, 105th Cong. (1998) (statement of L0pht Heavy Industries) 
Gates, Bill, "An Open Letter to Hobbyists" Various Sources 1975 http://en.wikipedia.org/wiki/Open\_Letter\_to\_Hobbyists
Habermas, Jurgen \emph{The Postnational Constellation} (Cambridge, Mass ; London: MIT Press 2001)
Habermas, Jurgen, "The Public Sphere: An Encyclopedia Article" \emph{New German Critique} (No 3. Autumn, 1974)  pp49-55
Headrick, Daniel. \emph{The Invisible Weapon} (New York: Oxford University Press, 1991)
Headrick, Daniel. \emph{When Information Came of Age.} (New York : Oxford University Press. 2000) pg.
Himanen, Pekka. \emph{The Hacker Ethic, and the Spirit of the Information Age}. (New York: Random House. 2001.)
Hollinger, Richard C. "Computer Hackers Follow A Guttman-Like Progression"  \emph{Phrack Magazine} (2.22 File 7 of 12. 1988)
Holt, Thomas J. "Subcultural Evolution? Examining the Influence of On and Off-line Experiences on Deviant Subcultures. \emph{Deviant Behavior} 28:2
IHTFP FAQ,  http://hacks.mit.edu/Hacks/misc/faq.html, accessed Feb 2013
Johns, Adrian. \emph{Piracy: The Intellectual Property Wars from Gutenberg to Gates}. (University of Chicago Press, 2010.)
Kelley, Kevin, \emph{What Technology Wants}, Viking 2010.
Kelty, Chris. \emph{Two Bits : The Cultural Significance of Free Software} (Durham: Duke University Press 2008). and Coleman, \emph{Coding Freedom.}
Kline, Katy, "A Brief Architectural History of MIT" in \emph{Art and Architecture at MIT: A Walking Tour of the Campus} (Cambridge: MIT Press, 1988)
Knappenberger, Brian, and John Dragonetti. \emph{We are legion the story of the hacktivists.} (Venice, California: Luminant Media 2012) and Sterling, Bruce \emph{The Hacker Crackdown: Law and disorder on the digital frontier} (Bantam, 1992)} 
Knight Lightning. \emph{Phrack World News.} Issue XV: Part One -  July 27, 1986} 
Knight Lightning, "Table of Contents" \emph{Phrack}, no 1. (March 1984)
McKeown, Nick and Phillip Levis, "Congestion Control - TCP Tahoe" (on-line lecture, Stanford, Fall 2012)} 
Mead, Margaret. \emph{Continuities in Cultural Evolution}. (New Haven: Yale University Press) 1964.
Net Market Share, "Market Share Statistics for Internet Technologies" http://www.netmarketshare.com/ and "Top 500 Supercomputer Sites" http://www.top500.org
Parker, Donn B, \emph{Fighting Computer Crime,} (New York: Scribner, 1983)
Parker, Donn B. et al, \emph{Computer Crime: Computer Security Techniques} (US DOJ Bureau of Justice Statistics and SRI International, 1982)
Raymond, Eric S. \emph{The Jargon File version 4.4.7} 2003 http://www.catb.org/jargon/html/H/hacker.html
Raymond, Eric S. \emph{The New Hacker's Dictionary - 3rd edition} (Cambridge: The MIT Press 1996)
Raymond, Eric S. "How To Become A Hacker". 20 May 2012. http://www.catb.org/esr/faqs/hacker-howto.html
Rosenbaum, Ron, "Secrets of the Little Blue Box" \emph{Esquire} 1971
Schroeder, Steve. \emph{The Lure the True Story of How the Department of Justice Brought Down Two of the World's Most Dangerous Cyber Criminals.} (Boston: Course Technology PTR. 2012) http://site.ebrary.com/id/10448180. 
Spinrad, Paul and Patti Meagher. "Project Genie: Berkeley’s piece of the computer revolution" \emph{Forefront} (Fall 2007) http://coe.berkeley.edu/news-center/publications/forefront/archive/forefront-fall-2007/features/berkeley2019s-piece-of-the-computer-revolution
Stallman, Richard. "Free Software: Freedom and Cooperation" (Speech Transcript. NYU. 29 May 2001.) http://www.gnu.org/events/rms-nyu-2001-transcript.txt
Stallman, Richard, "On Hacking" 2002. http://stallman.org/articles/on-hacking.html
Stallman, Richard. "On Hacking," 2002. http://stallman.org/articles/on-hacking.html
Stott, Jason. \emph{BBS: The Documentary} 2005.} 
Stott, Jason, "Textfiles.com File Statistics," Jul 1 2005, http://www.textfiles.com/filestats.html
"The Constitution of a Hacker." \emph{2600 Magazine.} (March 1984 V1 3)} 
The Mentor "The Hacker Manifesto" Jan 8, 1986 http://www.mithral.com/~beberg/manifesto.html
Thomas, Douglas, \emph{Hacker Culture} (Minneapolis: University of Minnesota 2002)
Torvalds, Linus, Richard Stallman, Bruce Perens, Eric S. Raymond, Larry M. Augustin, Brian Behlendorf, Michael Tiemann, Susan Egan, and J. T. S. Moore. \emph{Revolution OS: hackers, programmers \& rebels unite.} S.l.: Wonderview Productions. 2003
Torvalds, Linus. Usenet Posting in comp.os.minix 5 Oct 1991. http://www.cs.cmu.edu/~awb/linux.history.html Accessed 18 Feb 2013.
United States Congress, "The Effects of Nuclear War" by Lionel S. Johns, et al., (Washington, D.C.:GPO, 1979), http://ota.fas.org/reports/7906.pdf
Wark, McKenzie.\emph{A Hacker Manifesto.} (Cambridge, MA : Harvard University Press, 2004)} 
Weizenbaum, Joseph. "Science and the compulsive programmer." \emph{Computer Power and Human Reason.} (San Fransisco: W.H. Freeman and Company, 1976)}
