Raymond, Eric S. \emph{The Jargon File version 4.4.7} 2003 http://www.catb.org/jargon/html/H/hacker.html}
Kline, Katy, "A Brief Architectural History of MIT" in \emph{Art and Architecture at MIT: A Walking Tour of the Campus} (Cambridge: MIT Press, 1988)}
Thomas, Douglas, \emph{Hacker Culture} (Minneapolis: University of Minnesota 2002)} 
United States Congress, "The Effects of Nuclear War" by Lionel S. Johns, et al., (Washington, D.C.:GPO, 1979), http://ota.fas.org/reports/7906.pdf}
Raymond, Eric S. "How To Become A Hacker". 20 May 2012. http://www.catb.org/esr/faqs/hacker-howto.html}
Stallman, Richard, "On Hacking" 2002. http://stallman.org/articles/on-hacking.html}
Script kiddies is a hacker term for someone who manages to learn how to use premade tools to cause mayhem without understanding or even intending to learn about the principles that make them work.}
Coleman, Gabriela. \emph{Coding Freedom.} Princeton: Princeton University Press, 2013, pg17.}
Chaos Computer Congress. "Hackerethik," Berlin 2013. http://ccc.de/de/hackerethik}
Digital Equipment Corporation \emph{Digital Equipment Corporation: Nineteen Fifty-Seven to the Present.} (DEC Press. 1978) pg. 3}
Stallman, Richard. "On Hacking," 2002. http://stallman.org/articles/on-hacking.html}
Kelty, Chris. \emph{Two Bits : The Cultural Significance of Free Software} (Durham: Duke University Press 2008). and Coleman, \emph{Coding Freedom.}}
Holt, Thomas J. "Subcultural Evolution? Examining the Influence of On and Off-line Experiences on Deviant Subcultures. \emph{Deviant Behavior} 28:2
Schroeder, Steve. \emph{The Lure the True Story of How the Department of Justice Brought Down Two of the World's Most Dangerous Cyber Criminals.} (Boston: Course Technology PTR. 2012) http://site.ebrary.com/id/10448180. 
Parker, Donn B, \emph{Fighting Computer Crime,} (New York: Scribner, 1983)}
Himanen, Pekka. \emph{The Hacker Ethic, and the Spirit of the Information Age}. (New York: Random House. 2001.)}
Wark, McKenzie.\emph{A Hacker Manifesto.} (Cambridge, MA : Harvard University Press, 2004)} 
Raymond, Eric S. \emph{The New Hacker's Dictionary - 3rd edition} (Cambridge: The MIT Press 1996)}
IHTFP FAQ,  http://hacks.mit.edu/Hacks/misc/faq.html, accessed Feb 2013}
Headrick, Daniel. \emph{When Information Came of Age.} (New York : Oxford University Press. 2000) pg.}
Headrick, Daniel. \emph{The Invisible Weapon} (New York: Oxford University Press, 1991)}
Abbate, Janet, \emph{Inventing the Internet} (Cambridge: MIT Press, 1999)}
Weizenbaum, Joseph. "Science and the compulsive programmer." \emph{Computer Power and Human Reason.} (San Fransisco: W.H. Freeman and Company, 1976)}  
Spinrad, Paul and Patti Meagher. "Project Genie: Berkeley’s piece of the computer revolution" \emph{Forefront} (Fall 2007) http://coe.berkeley.edu/news-center/publications/forefront/archive/forefront-fall-2007/features/berkeley2019s-piece-of-the-computer-revolution}
Abbate, Janet, \emph{Inventing the Internet} (Cambridge: MIT Press, 1999)}
Breen, C. and Dahlbom, C. A. "Signaling Systems for Control of Telephone Switching," \emph{The Bell System Technical Journal} 39:6. Nov 1960.}
Rosenbaum, Ron, "Secrets of the Little Blue Box" \emph{Esquire} 1971}

Johns, Adrian. \emph{Piracy: The Intellectual Property Wars from Gutenberg to Gates}. (University of Chicago Press, 2010.)}
Gates, Bill, "An Open Letter to Hobbyists" Various Sources 1975 http://en.wikipedia.org/wiki/Open\_Letter\_to\_Hobbyists}
Stott, Jason. \emph{BBS: The Documentary} 2005.} 
Stott, Jason, "Textfiles.com File Statistics," Jul 1 2005, http://www.textfiles.com/filestats.html}
Parker, Donn B. et al, \emph{Computer Crime: Computer Security Techniques} (US DOJ Bureau of Justice Statistics and SRI International, 1982)}
Knight Lightning, "Table of Contents" \emph{Phrack}, no 1. (March 1984)}
Knight Lightning. \emph{Phrack World News.} Issue XV: Part One -  July 27, 1986} 
youth of tomorrow.ibid. Issue XVIV/1. 1988.}\end{quote}
Hollinger, Richard C. "Computer Hackers Follow A Guttman-Like Progression"  \emph{Phrack Magazine} (2.22 File 7 of 12. 1988)}
"The Constitution of a Hacker." \emph{2600 Magazine.} (March 1984 V1 3)} 
Knappenberger, Brian, and John Dragonetti. \emph{We are legion the story of the hacktivists.} (Venice, California: Luminant Media 2012) and Sterling, Bruce \emph{The Hacker Crackdown: Law and disorder on the digital frontier} (Bantam, 1992)} 
DIzzIE, "Why I Steal from Libraries" (Textfiles.com 2007) http://textfiles.com/uploads/diz-libraries.txt} 
\emph{Government Computer Security: Weak Computer Security in the Government: Is the Public at Risk with the U.S. Permanent Subcommittee on Investigations of the Senate Committee on Governmental Affairs}, 105th Cong. (1998) (statement of L0pht Heavy Industries) }
Stallman, Richard. "Free Software: Freedom and Cooperation" (Speech Transcript. NYU. 29 May 2001.) http://www.gnu.org/events/rms-nyu-2001-transcript.txt}
Torvalds, Linus. Usenet Posting in comp.os.minix 5 Oct 1991. http://www.cs.cmu.edu/~awb/linux.history.html Accessed 18 Feb 2013.}\end{quote}
McKeown, Nick and Phillip Levis, "Congestion Control - TCP Tahoe" (on-line lecture, Stanford, Fall 2012)} 
Torvalds, Linus, Richard Stallman, Bruce Perens, Eric S. Raymond, Larry M. Augustin, Brian Behlendorf, Michael Tiemann, Susan Egan, and J. T. S. Moore. \emph{Revolution OS: hackers, programmers \& rebels unite.} S.l.: Wonderview Productions. 2003}
Habermas, Jurgen, "The Public Sphere: An Encyclopedia Article" \emph{New German Critique} (No 3. Autumn, 1974)  pp49-55}
Habermas, Jurgen \emph{The Postnational Constellation} (Cambridge, Mass ; London: MIT Press 2001)}
Kelley, Kevin, \emph{What Technology Wants}, Viking 2010.}
Mead, Margaret. \emph{Continuities in Cultural Evolution}. (New Haven: Yale University Press) 1964.}
The Mentor "The Hacker Manifesto" Jan 8, 1986 http://www.mithral.com/~beberg/manifesto.html}
Net Market Share, "Market Share Statistics for Internet Technologies" http://www.netmarketshare.com/ and "Top 500 Supercomputer Sites" http://www.top500.org}
Brautigan, Richard. "All Watched Over by Machines of Loving Grace". San Francisco. The Communication Company. 1967. Print.}